Think deep for reef resilience

### 2025-08-09 paper/paper_draft.qmd
Fix typo and more "natural" description of nlog scale
Correct typo: assignemnt -> assignment

Correct grammar: "source - to - sink" (using em dash, with space) to "source-to-sink" (en dash, no space).

![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
Green indicates a low cover cluster assignemnt, orange represents a medium cover assignment
and blue represents assignment of a reef to a high coral cover cluster. The vertical width
of reef elements varies depending on the number of reefs within the bioregion (displayed in
the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
ACCESS-CM2, NorESM2-MM and
GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. Point colour represents log (natural) scaled reef total connectivity strength.
Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
clusters with the highest median area-relative cover between 2030 and 2040 within each
bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
width="14.82cm"}

@@

![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median log (natural) source – to – sink ratio for
each cluster and grey points represent the ratio value for each reef. Vertical grey lines
represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
incoming connectivity levels. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
width="14.82cm"}

![Log (natural) total connectivity strength for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
violin represent the median log (natural) total connectivity strength for each cluster.
Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
width="14.82cm"}

>>>>

![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
Green indicates a low cover cluster assignment, orange represents a medium cover assignment
and blue represents assignment of a reef to a high coral cover cluster. The vertical width
of reef elements varies depending on the number of reefs within the bioregion (displayed in
the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
ACCESS-CM2, NorESM2-MM and
GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef natural log of
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. Colour of each point represents the natural log of scaled reef total connectivity
strength. Displays results from median timeseries using
ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
width="14.82cm"}

@@

![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
clusters with the highest median area-relative cover between 2030 and 2040 within each
bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
percentile confidence intervals. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
width="14.82cm"}

@@

![Source-to-sink connectivity ratios (in natural log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median source-to-sink ratio for each cluster and grey
points represent the ratio value for each reef. Vertical grey lines represent a
source-to-sink ratio of 0 (in natural log scale) indicating equal outgoing and incoming
connectivity levels. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
width="14.82cm"}

![Total connectivity strength (in natural log scale) for reefs within each bioregion,
separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2040 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
lines within each violin represent the median natural log of total connectivity strength for
each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
width="14.82cm"}
